---
title: "Bridge Data Explaratory"
author: "Yanshi Luo"
date: "2/5/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Name: Yanshi Luo
#### Email: yluo82@wisc.edu

---

## The Total Average Daily Traffic of the bridges in each state & The number of the bridges of each state

For the item recorded, we can see the `NBI Record Format` page.
[NBI Record Format](https://www.fhwa.dot.gov/bridge/nbi/format.cfm)

About the data

Since the file is too large, I cannot upload it to the Github. Please save the data from the `downloadBridges.R` with `save(M, file = "./data/tidyBridge.RData")` to save the data into the work directory.

```{r}
# Questions:
# For the bridges data, what variables are you interested in? 
# Select, filter, and plot. Do something different from my code! 
# Make several plots. Save several pdfs and push to github.

library(ggplot2)
library(dplyr)

# I store the variable `M` in `downloadBridges.R` into 
# `tidyBridge.Rdata` file and load it here
load(file = "data/tidyBridge.RData")

# # Since the file is too large, I cannot upload it to the Github.
# # Please save the data from the `downloadBridges.R`
# save(M, file = "tidyBridge.RData")
# # to save the data into the work directory.
```

The columns that I may interested in:
* 6	Latitude
* 17	Longitude
* 27	Year Built
* 29	Average Daily Traffic
* 30	Year Of Average Daily Traffic

Using `grep()` to search the column name and use `select` to pick them up.

```{r}
colnames(M)[grep("006|017|027|029|030", colnames(M))]

# Get the data
M %>% select(STATE_CODE_001, COUNTY_CODE_003, LAT_016, LONG_017, ADT_029) %>%
  mutate(code = STATE_CODE_001*1000+COUNTY_CODE_003) -> D1
D1%>% group_by(STATE_CODE_001) %>% dplyr::summarise(count = n(), totalADT = sum(ADT_029))-> d

# install.packages("tidyr")
# library(tidyr)
# d %>% gather(amount, value, -STATE_CODE_001)


library(ggplot2)

# The totalADT of the bridges in each state.
ggplot(d, aes(x=STATE_CODE_001)) + 
  geom_bar(aes(y = totalADT), stat="identity") + 
  labs(title="Plot of totalADT", 
       x="State Code", y = "Total Average Daily Traffic")


# The count of the bridges of each state.
ggplot(d, aes(x=STATE_CODE_001)) + 
  geom_bar(aes(y = count), stat="identity") + 
  labs(title="Plot of Bridges Count", 
       x="State Code", y = "Number of Bridges")
```

## Visualization with Leaflet(Without running here)
I searched in the google map to clear the LAT and LONG format

I tried some method to deal with them and I find out that (31061110 87341340) means (31.061110, -87341340)

So I tidied the data as follows,

```{r, eval=F}
library(stringr)
D1$code <- str_pad(D1$code, 5, pad = "0")
D1%>% group_by(code) %>% dplyr::summarise(count = n())


D1 %>% mutate(LAT = LAT_016/1000000, LONG = LONG_017/-1000000) %>%
  select(STATE_CODE_001, code, LAT, LONG)-> d2


#############################################################################
# PLEASE DO NOT RUN THE FOLLOWING CODE ON YOUR COMPUTER UNLESS YOU WOULD LIKE TO
# SPEND 20 MINUTED TO WAIT FOR ITS LOADING!!!!
# IT IS VERY EASY TO CRASH!!!! SINCE THERE ARE TOO MAY DATA!!!
# I ran it on my own Ubuntu Rstudio sever to do my own job when the map is drawing.
###########################################################################
# This is a leaflet interactive map.
# The idea comes from:
# https://www.kaggle.com/taddallas/d/kaggle/college-scorecard/interactive-map
#
# I tried a lot of time to modify the data but it keeps crashing until I 
#     finally figure out the lantitude and lontitude data format.
# In fact, it crashes so many time that I failed to hand in my final work beore 12 pm T_T
# A sad story.........
##########################################################################

library(leaflet)

## filter data
d2<-filter(d2,
           is.na(code)==FALSE &       ## Key measurements aren't missing
             is.na(LAT)==FALSE &
             is.na(LONG)==FALSE &
             LAT>20 & LAT<50 &         ## Location is US 48
             LONG>(-130) & LONG<(-60))


m <- leaflet(d2) %>%
  setView(-93.65, 42.0285, zoom = 4) %>%
  addTiles() %>%
  addMarkers(lat = ~LAT, lng = ~LONG,
             options = popupOptions(closeButton = TRUE),
             clusterOptions = markerClusterOptions())


m
```



